Fusion Moves for Correlation Clustering

### 2014-10-31 paper/egpaper_for_review.tex
text social networks

>>>>

\subsection{Social Networks}
A application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{http://snap.stanford.edu/data/index.html}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ is the edge-weight is positive or negative, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The first network is called \emph{Slashdot}. 
Slashdot is a technology-related news website know for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.

We consider the problem to cluster this graphs such that positively weighted edges link inside and negatively weighted between clusters.
In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
% 
To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
\begin{align}
  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
\end{align}
We define the following energy function
\begin{align}
 J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
\end{align}
which is zero if the given partitioning does not violated any relation and larger otherwise.
